### 2016-07-06 intro.tex
adding related work
syntax, new auth notes

\tsnote{Perhaps a more obvious way to capture the idea that ``finding
  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say
that that the adversary wins iff it outputs~$f$ FPs (these may have
been previously queried to the set-membership oracle).  
Note that in the ROM (and probably in practice) finding~$f>1$ FPs will
require~$f$ times the work.  Right?} 
%\tsnote{Here's an off-the-wall idea.  What if the basic FP security
%notion gave the adversary an oracle for set-membership (and the hash functions, depending on the setting), and after interacting with these
%it is challenged with either $x_0$ or $x_1$, where $x_0$ is a random
%point from the set of non-FPs, and $x_1$ is a random point from the
%set of FPs?  (No oracles after being challenged.)  The adversary has
%to decide which it received.}

@@

\heading{Related work: tangential}
\begin{itemize}
\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
\item Dodis et al. ``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
\end{itemize}

>>>>

\tsnote{Perhaps a more obvious way to capture the idea that ``finding
  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say
that that the adversary wins iff it outputs~$f$ FPs (these may have
been previously queried to the set-membership oracle).  
Note that in the ROM (and probably in practice) finding~$f>1$ FPs will
require~$f$ times the work.  Right?} \tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}
%\tsnote{Here's an off-the-wall idea.  What if the basic FP security
%notion gave the adversary an oracle for set-membership (and the hash functions, depending on the setting), and after interacting with these
%it is challenged with either $x_0$ or $x_1$, where $x_0$ is a random
%point from the set of non-FPs, and $x_1$ is a random point from the
%set of FPs?  (No oracles after being challenged.)  The adversary has
%to decide which it received.}

@@

\heading{Related work: tangential}
\begin{itemize}
\item Chang and Mitzenmacher ``Privacy Preserving Keyword Searches on Remote Encrypted Data''.
\item Mitzenmacher and Vadhan. ``Why Simple Hash Functions Work: Exploiting the Entropy in a Data Stream''.
\item Dodis et al. ``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
\end{itemize}
